
---
title: "Problem2"
output:
  pdf_document:
    keep_tex: true
    latex_engine: xelatex
header-includes:
  - \usepackage{wrapfig}
---



```{r setup, include=FALSE}
library(readxl)#laod data from excel file
library(corrplot)
library(arules)
library(arulesViz)
wd = getwd()
loan = read_excel(paste(wd,"/loan.xls",sep=""),sheet = 'Data',skip = 2,)
loan = loan[,-1]
summary(loan)
```

##(a)Explore the demographic information of the customers.
```{r,include=FALSE}
dgc = as.data.frame(loan[,c(1,2,3,5,7)]) #avoid shallow copy.
```

```{r,include = TRUE, echo = FALSE,fig.show='hold',out.height = "40%",out.width="30%"}
hist(dgc$Age)
hist(dgc$Experience)
hist(dgc$Income)
counts<-table(loan$Family)
barplot(counts,main="loan$Family",xlab="family",ylab="Frequency",col="white")
counts<-table(loan$Education)
barplot(counts,main="loan$Education",xlab="education",ylab="Frequency",col="white")
```
\subsection{(b)Analyze what variables possibly make a customer more likely to accept a personal loan?}

```{r exa, echo = FALSE, fig.env="wrapfigure",include=FALSE}
corrplot(cor(loan),method="shade",diag = FALSE,addgrid.col = "white",tl.col = "black",tl.cex = 0.5,cl.cex = 0.5)
```
\begin{wrapfigure}{r}{0.7\textwidth} 
  \includegraphics{tem_files/figure-latex/exa-1.pdf}
  \caption{Correalation Among Variables}
\end{wrapfigure}
  Starting from left to right, the first pair that demonstates a high correlation is "Age-Experience". However, it is apparent that people tend to gain more professional experience as they grow up. 

```{r shopbasket,include = FALSE , echo=FALSE,fig.show='hold',fig.env="wrapfigure"}
basket = as.data.frame(loan[,8:13])
basket = +(basket>0)
item_list = c("Mortage","PersonalLoan","SecuritiesAccount","CDAccount","Online","CreditCard")
ndt = basket
basket.sum = apply(basket,1,sum)
ndt = basket[basket.sum>1,]
dimnames(ndt) = list(c(1:nrow(ndt)),item_list)

ndt = as(ndt,"transactions")
summary(ndt)
rules <- apriori(ndt, parameter = list(supp = 0.1, conf = 0.1, minlen=2, target = "rules"))
inspect(head(rules, by = "lift"))
plot(rules, method="graph", control=list(type="items") )
plot(x=rules,method = 'paracoord')
```